---
title: "PA1_template.Rmd\U0001D681\U0001D696\U0001D68D"
author: "Donbenoni"
date: "15 November 2017"
output: html_document
---
# Code for reading in the dataset and/or processing the data

```{r}
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", destfile = "Actmon.zip" )
unzip("actmon.zip")
filex <- read.csv("activity.csv", header = TRUE)
filex$date<-as.Date(filex$date)
totalstepsperday <- aggregate(steps ~ date, data = filex, FUN = sum, na.rm = TRUE)
```

# Histogram of the total number of steps taken each day

```{r}
hist(totalstepsperday$steps, breaks = 25, main = "Total Steps Per Day", xlab = "Number of steps per day", ylab = "Frequency", col = "Magenta")
```

# Mean and median number of steps taken each day

```{r}
totalstmean <- mean(totalstepsperday$steps)
totalstmedian <- median(totalstepsperday$steps)
```

## Call mean and median
```{r}
totalstmean
```
```{r}
totalstmedian

```

# Time series plot
## Time series plot of the average number of steps taken
```{r}
avgstepstkn <- aggregate(filex$steps, by=list(filex$interval), FUN=mean, na.rm=TRUE)
colnames(avgstepstkn) <- c("Interval", "Steps")
library(ggplot2)
ggplot(aes(x = Interval, y = Steps), data = avgstepstkn) + geom_line() + theme_bw()
```

# The 5-minute interval that, on average, contains the maximum number of steps
```{r}
avgstepstkn[avgstepstkn$Steps==max(avgstepstkn$Steps),1]
```
# Code to describe and show a strategy for imputing missing data
## Calculate number of NA's in data
```{r}
sum(is.na(filex$steps))
```
## Remove NA's
```{r}
filex$steps[is.na(filex$steps)] <- mean(filex$steps, na.rm = TRUE)
```
## See if NA's are removed
```{r}
sum(is.na(filex$steps))
```
# Histogram of the total number of steps taken each day after missing values are imputed
```{r}
Totsteps <- aggregate(filex$steps, by = list(filex$date), FUN = sum, na.rm = TRUE)
hist(Totsteps$x, breaks = seq(from = 0, to = 25000, by = 2500), col = "red", xlab = "Number of steps taken", ylim = c(0,30), main = "Total number of steps taken each day after missing values are imputed")
```
## Mean and median of data without NA's
```{r}
mean(Totsteps$x)
```
```{r}
median(Totsteps$x)
```

# Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
# Convert into days of the week.
filex$days=tolower(weekdays(filex$date))
filex$day_type <- ifelse(filex$days == "saturday" | filex$days == "sunday", "weekend", "weekday")

# Mean steps taken
avgst2 <- aggregate(filex$steps, by = list(filex$interval, filex$day_type), FUN = mean, na.rm=TRUE)
colnames(avgst2) <- c("interval","day_type","steps")

# Load ggplot for Panel plot
library(ggplot2)
ggplot(aes(x = interval, y = steps), data = avgst2) + geom_line() + facet_wrap( ~ avgst2$day_type) + theme_dark()
```

